The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$

### 2015-05-18 formalwriteup.tex
Move singular vector

As described in \cite[Section 2.5]{BC1}, there is a contravariant form 
\[
\beta_c: \Sym(\h^*) \otimes \Sym(\h) \to k
\]
defined by setting $\beta_c(1, 1) = 1$ and imposing for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in \Sym(\h)$ that
\[
\beta_c(xf,g)=\beta_c(f,xg) \qquad \text{ and } \qquad \beta_c(f,yg) = \beta_c(yf,g).
\]
Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J = \ker(\beta_c)$, and the quotient $L = A/J$ is an irreducible representation of $\HH_{\hbar,c}(\h)$.  It inherits a $\ZZ_{\geq 0}$-grading from $A$, and we recall that its Hilbert series is 
\[
h_L(t) = \sum_{j \geq 0} \dim L_j t^j,
\]
where $L_j$ is the degree $j$ subspace of $L$.

@@

For a formal Laurent series $r(z)$, we denote by $[z^l] r(z)$ the coefficient of $z^l$ in $r(z)$.  For $i = 0, \ldots, n - 2$, define the formal power series
\[
F_i(z)=\frac{1}{1-x_iz} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right),
\]
and consider the coefficients $f_i = [z^p] F_i(z)$.

@@

We let $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$ and $F(z)$ be the formal power series in $z$ defined by
\[
F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).
\]
where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$. 
Let $F_i(z)$ for $i=0,\dots,n-1$ be $\frac{F(z)}{1-x_iz}$ and $f_i=[z^p]F_i(z)$. The $f_i$ will be the generators of the maximal ideal $J$.

Because of the definition of the contravariant form $\beta_c$, showing that an element $f$ of $A$ is in the kernel of $\beta_c$ is equivalent to showing that the Dunkl operators corresponding to the basis elements of $\h$ annihilate $f$.

\begin{proposition}\label{prop:ann} The elements $f_i$ for $i=0,\dots,n-1$ are annihilated by $D_i-D_j$ for all $i \ne j$.
\end{proposition}

>>>>

As described in \cite[Section 2.5]{BC1}, there is a contravariant form 
\[
\beta_c: \Sym(\h^*) \otimes \Sym(\h) \to k
\]
defined by setting $\beta_c(1, 1) = 1$ and imposing for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in \Sym(\h)$ that
\[
\beta_c(xf,g)=\beta_c(f,xg) \qquad \text{ and } \qquad \beta_c(f,yg) = \beta_c(yf,g).
\]
Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J = \ker(\beta_c)$.  By the definition of $\beta_c$, $J$ is generated by homogeneous vectors $f \in A$ killed by all Dunkl operators $D_y$.  Such $f$ are known as \textit{singular vectors}.

The quotient $L = A/J$ is an irreducible representation of $\HH_{\hbar,c}(\h)$.  It inherits a $\ZZ_{\geq 0}$-grading from $A$, and we recall that its Hilbert series is 
\[
h_L(t) = \sum_{j \geq 0} \dim L_j t^j,
\]
where $L_j$ is the degree $j$ subspace of $L$.

@@

For a formal Laurent series $r(z)$, we denote by $[z^l] r(z)$ the coefficient of $z^l$ in $r(z)$.  For $i = 0, \ldots, n - 2$, define the formal power series
\[
F_i(z)=\frac{1}{1-x_iz} \left(\sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right),
\]
where $\binom{c}{k} = \frac{c (c - 1) \cdots (c - k + 1)}{k!}$ and consider the coefficients $f_i = [z^p] F_i(z)$.

@@

Define $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$ and $F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g(z)-1)^k\right)$ so that $F_i(z) = \frac{F(z)}{1-x_iz}$ and $f_i = [z^p] \frac{F(z)}{1-x_iz}$.  We now show that $f_i$ are singular vectors.
\begin{proposition}\label{prop:ann} 
The elements $f_i$ for $i=0,\dots,n-1$ singular vectors in $A$.
\end{proposition}
\begin{proof}
We must show that $f_i$ is annihilated by annihilated by $D_j-D_l$ for all $j \ne l$.
